MCTS Based on Simple Regret

### 2012-02-22 slides/slides.tex
empirical evaluation in progress

\begin{frame}{Doing better than UCT on sets}
\begin{figure}[h]
\centering
\includegraphics[scale=0.8]{onelevel-tree.pdf}
\end{figure}
When an arm is selected based on the {\bf sample mean}:
\begin{itemize}
\item Regret of UCB decreases {\it polynomially} with $n$.
\item Regret of $\epsilon$-greedy decreases {\it exponentially} with
  $n$.
\item Regret of UVB: $\max V_i$, $V_{i_{best}}=\frac {1-1/k}
  {n_{i_{best}}},\quad V_{i_{other}}=\frac {1/k} {n_{i_{other}}}$
  decreases exponentially with $n$, faster than $\epsilon$-greedy.
\end{itemize}
\end{frame}

>>>>

\begin{frame}{Simple regret in MAB}

\begin{figure}[h]
  \begin{minipage}[c]{0.4\linewidth}
    \centering
    \includegraphics[scale=0.65]{onelevel-tree.pdf}\\
    {\tiny Fig. 1: Search tree}
  \end{minipage}
  \begin{minipage}[c]{0.4\linewidth}
    \centering
    \includegraphics[scale=0.4]{flat-trilevel-k=64-uqb=8.pdf}\\
    {\tiny Fig. 2: Regret vs number of samples}
  \end{minipage}
  \label{fig:mab-simple-regret}
\end{figure}
\begin{itemize}
\item For smaller numbers of
samples, $\frac 1 2$-greedy achieves the best
performance.
\item For larger numbers of samples, UCB$_{\sqrt{\cdot}}$
outperforms $\frac 1 2$-greedy. 
\item A combination of $\frac 1
2$-greedy  and UCB$_{\sqrt{\cdot}}$ dominates UCB over the
whole range.
\end{itemize}
\end{frame}
